INTELLIGENT SYSTEMS

### 2021-04-11 paper_6.tex
finish 6.4.4

>>>>

\subsubsection{Semantic Segmentation Results}
\begin{enumerate}
    \item \emph{Impact of the mask quality}: as shown in Table \ref{IoU}, the various processing 
    steps lead to a constant increase in the IoU index. In particular, 
    the value reached by the index is that relating to the first round of 
    network training, therefore we proceed recursively with the training of 
    the network so that it can produce a better mask.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c|c|}
            \hline
            Training Mask Type & IoU(\%)\\
            \hline
            Coarse Masks & 32.5 \\
            Bounding Boxes & 35.2 \\
            Enhanced Masks & 47.7 \\
            Refined Masks & 50.4 \\
            \hline
        \end{tabular}
        \end{adjustbox}
        \caption{THe performance of semantic segmentation networks evalueted in the validation split of PASCAL VOC dataset in the mean IoU.}
        \label{IoU}
    \end{table}

    \item \emph{Effectiveness of recursive refinement}: the evaluation of each refined 
    mask takes place using two types of masks, with or without application 
    of the GrabCut. Between two rounds the masks are improved 
    with a post-processing process by three strategies: a) If the pixels in 
    the foreground are less than 1\% and greater than 80\%, then this image 
    will be discarded by the next training round. b) All the pixels 
    of the original image, labeled with a category must correspond to the 
    predicted pixels with the same category, otherwise these will be considered 
    as background pixels. c) In recursive training, the GrubCut 
    method is applied to the masks that the DeepLab model predicted to 
    have improved masks. In figure \ref{fig:GrubCutApp} it can be seen that the application 
    of GrubCut increases the IoU value and also the system saturates after 
    5 training rounds.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.8 \linewidth]{images/paper6/GrabCut.png}
        \centering
        \caption{Enhancement with GrubCut application}
        \label{fig:GrubCutApp}
    \end{figure}

    \item \emph{Comparison with others}: The performance comparison is carried out on both the validation and test sets of the PASCAL VOC dataset (Fig. \ref{fig:IoU score comparison}). In the state of the art, models trained with methods based on object-level labels annotation obtain a better score (greater than 60\%) than models trained with methods that have an annotation of the type image-level labels. The proposed model, on the other hand, while using the image-level labels annotation method, achieves an average IoU score greater than 60\% on both the evaluation and test sets. However, there are several classes in which the model obtains a low IoU value (Fig. \ref{fig:classes}).
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.6 \linewidth]{images/paper6/comparison.png}
        \centering
        \caption{Comparison, in terms of IoU score, between different models.}
        \label{fig:IoU score comparison}
    \end{figure}
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 1 \linewidth]{images/paper6/classes.png}
        \centering
        \caption{Score of IoU in some classes.}
        \label{fig:classes}
    \end{figure}
\end{enumerate}

\subsubsection{Qualitative Results}
